A Heuristic Approach towards Drawings of Graphs with High Crossing Resolution

### 2019-08-05 paper/journal.tex
Last changes.

Since all algorithms of the experiment can easily be adjusted to maximize~only the crossing resolution, or only the angular resolution or both (by maximizing~the total resolution), we adjusted each of them to maximize exclusively the corresponding measures. In our algorithm, this can be achieved by modifying appropriately the content of the vertex-pool (as we discussed in Section~\ref{ssec:variants}), while in the algorithms of Argyriou et al.\ and of Huang et al.\ by switching on only the forces that maximize the corresponding properties under measure (note that, each of these two algorithms has a different set of forces to maximize the crossing and the angular resolution, such that together they maximize the total resolution). The reported results, illustrated in Figures~\ref{fig:cr-res}--\ref{fig:northAngular}, are on average across different drawings with same number of vertices on the following set of parameters:
%
\begin{enumerate}[P.1.]
\item \label{p:cr-res} crossing resolution
\item \label{p:to-res} total resolution
\item \label{p:an-res} angular resolution
\item \label{p:as-rat} edge-length ratio
\item \label{p:no-xing} number of crossings
\end{enumerate}

@@

In this subsection, we report the results of our expertimental evaluation for the non-planar Rome graphs. Note that we did not impose any grid constraint on our algorithms. Our results are summarized in Figures~\ref{fig:cr-res}, \ref{fig:an-res} and~\ref{fig:to-res}.

@@

% ==================================================================
%\input{cr-res-north.tex}
% ==================================================================
\begin{figure*}[t!]
	\centering
	\subfloat[\label{fig:northCrossing-1}{Crossing resolution vs no.~of vertices}]{
	\includegraphics[scale=0.99,page=1]{figures/north}}
	\hfil
	\subfloat[\label{fig:northCrossing-2}{Edge-length ratio vs no.~of vertices}]{
	\includegraphics[scale=0.99,page=2]{figures/north}}

	\subfloat[\label{fig:northCrossing-3}{No.~of crossings vs no.~of vertices}]{
	\includegraphics[scale=0.99,page=3]{figures/north}}
	\hfil
	\subfloat[\label{fig:northCrossing-4}{No.~of iterations vs no.~of vertices}]{
	\includegraphics[scale=0.99,page=4]{figures/north}}
	\caption{Experimental results for the crossing resolution on the AT\&T graphs.}
	\label{fig:northCrossing}
\end{figure*}

% ==================================================================
%\input{to-res-north.tex}
% ==================================================================
\begin{figure*}[t!]
	\centering
	\subfloat[\label{fig:northTotal-1}{Total resolution vs no.~of vertices}]{
	\includegraphics[scale=0.99,page=5]{figures/north}}
	\hfil
	\subfloat[\label{fig:northTotal-2}{Edge-length ratio vs no.~of vertices}]{
	\includegraphics[scale=0.99,page=6]{figures/north}}

	\subfloat[\label{fig:northTotal-3}{No.~of crossings vs no.~of vertices}]{
	\includegraphics[scale=0.99,page=7]{figures/north}}
	\hfil
	\subfloat[\label{fig:northTotal-4}{No.~of iterations vs no.~of vertices}]{
	\includegraphics[scale=0.99,page=8]{figures/north}}
	\caption{Experimental results for the total resolution on the AT\&T graphs.}
	\label{fig:northTotal}
\end{figure*}

% ==================================================================
%\input{an-res-north.tex}
% ==================================================================
\begin{figure*}[t!]
	\centering
	\subfloat[\label{fig:northAngular-1}{Angular resolution vs no.~of vertices}]{
	\includegraphics[scale=0.99,page=9]{figures/north}}
	\hfil
	\subfloat[\label{fig:northAngular-2}{Edge-length ratio vs no.~of vertices}]{
	\includegraphics[scale=0.99,page=10]{figures/north}}

	\subfloat[\label{fig:northAngular-3}{No.~of crossings vs no.~of vertices}]{
	\includegraphics[scale=0.99,page=11]{figures/north}}
	\hfil
	\subfloat[\label{fig:northAngular-4}{No.~of iterations vs no.~of vertices}]{
	\includegraphics[scale=0.99,page=12]{figures/north}}
	\caption{Experimental results for the angular resolution on the AT\&T graphs.}
	\label{fig:northAngular}
\end{figure*}

% ==================================================================
\input{grid-rome.tex}
% ==================================================================

>>>>

Since all algorithms of the experiment can easily be adjusted to maximize~only the crossing resolution, or only the angular resolution or both (by maximizing~the total resolution), we adjusted each of them to maximize exclusively the corresponding measures. In our algorithm, this can be achieved by modifying appropriately the content of the vertex-pool (as we discussed in Section~\ref{ssec:variants}), while in the algorithms of Argyriou et al.\ and of Huang et al.\ by switching on only the forces that maximize the corresponding properties under measure (note that, each of these two algorithms has a different set of forces to maximize the crossing and the angular resolution, such that together they maximize the total resolution). The reported results, illustrated in Figures~\ref{fig:cr-res}--\ref{fig:northAngular}, are on average across different drawings with same number of vertices on the following set of parameters:
%
\begin{enumerate}[P.1.]
\item \label{p:cr-res} crossing resolution
\item \label{p:to-res} total resolution
\item \label{p:an-res} angular resolution
\item \label{p:as-rat} edge-length ratio
\item \label{p:no-xing} number of crossings
\end{enumerate}
%
Each bold-drawn curve corresponds to the mean values. The two same-colored curves above and below represent the upper and the lower standard deviation, respectively.

@@

In this subsection, we report the results of our expertimental evaluation for the non-planar Rome graphs. Note that we did not impose any grid constraint on our algorithms. Our results are summarized in Figures~\ref{fig:cr-res}, \ref{fig:to-res} and~\ref{fig:an-res}.

@@

% ==================================================================
%\input{cr-res-north.tex}
% ==================================================================
\begin{figure*}[t!]
	\centering
	\subfloat[\label{fig:northCrossing-1}{Crossing resolution vs no.~of vertices}]{
	\includegraphics[scale=0.99,page=1]{figures/north_colored}}
	\hfil
	\subfloat[\label{fig:northCrossing-2}{Edge-length ratio vs no.~of vertices}]{
	\includegraphics[scale=0.99,page=2]{figures/north_colored}}

	\subfloat[\label{fig:northCrossing-3}{No.~of crossings vs no.~of vertices}]{
	\includegraphics[scale=0.99,page=3]{figures/north_colored}}
	\hfil
	\subfloat[\label{fig:northCrossing-4}{No.~of iterations vs no.~of vertices}]{
	\includegraphics[scale=0.99,page=4]{figures/north_colored}}
	\caption{Experimental results for the crossing resolution on the AT\&T graphs.}
	\label{fig:northCrossing}
\end{figure*}

% ==================================================================
%\input{to-res-north.tex}
% ==================================================================
\begin{figure*}[t!]
	\centering
	\subfloat[\label{fig:northTotal-1}{Total resolution vs no.~of vertices}]{
	\includegraphics[scale=0.99,page=9]{figures/north_colored}}
	\hfil
	\subfloat[\label{fig:northTotal-2}{Edge-length ratio vs no.~of vertices}]{
	\includegraphics[scale=0.99,page=10]{figures/north_colored}}

	\subfloat[\label{fig:northTotal-3}{No.~of crossings vs no.~of vertices}]{
	\includegraphics[scale=0.99,page=11]{figures/north_colored}}
	\hfil
	\subfloat[\label{fig:northTotal-4}{No.~of iterations vs no.~of vertices}]{
	\includegraphics[scale=0.99,page=12]{figures/north_colored}}
	\caption{Experimental results for the total resolution on the AT\&T graphs.}
	\label{fig:northTotal}
\end{figure*}

% ==================================================================
%\input{an-res-north.tex}
% ==================================================================
\begin{figure*}[t!]
	\centering
	\subfloat[\label{fig:northAngular-1}{Angular resolution vs no.~of vertices}]{
	\includegraphics[scale=0.99,page=5]{figures/north_colored}}
	\hfil
	\subfloat[\label{fig:northAngular-2}{Edge-length ratio vs no.~of vertices}]{
	\includegraphics[scale=0.99,page=6]{figures/north_colored}}

	\subfloat[\label{fig:northAngular-3}{No.~of crossings vs no.~of vertices}]{
	\includegraphics[scale=0.99,page=7]{figures/north_colored}}
	\hfil
	\subfloat[\label{fig:northAngular-4}{No.~of iterations vs no.~of vertices}]{
	\includegraphics[scale=0.99,page=8]{figures/north_colored}}
	\caption{Experimental results for the angular resolution on the AT\&T graphs.}
	\label{fig:northAngular}
\end{figure*}

% ==================================================================
%\input{grid-rome.tex}
% ==================================================================
\begin{figure*}[t!]
	\centering
	\subfloat[\label{fig:crossingResolutionGrid}{Crossing resolution vs no.~of vertices}]{
	\includegraphics[scale=0.99,page=1]{figures/grid_colored}}
	\hfil
	\subfloat[\label{fig:crossingResolutionAspectRatioGrid}{Edge-length ratio vs no.~of vertices}]{
	\includegraphics[scale=0.99,page=2]{figures/grid_colored}}

	\subfloat[\label{fig:crossingResolutionCrossingNumberGrid}{No.~of crossings vs no.~of vertices}]{
	\includegraphics[scale=0.99,page=3]{figures/grid_colored}}
	\hfil
	\subfloat[\label{fig:crossingResolutionTimeGrid}{No.~of iterations vs no.~of vertices}]{
	\includegraphics[scale=0.99,page=4]{figures/grid_colored}}
	\caption{Experimental results for the angular resolution on the AT\&T graphs.}
	\label{fig:experimentsGrid}
\end{figure*}
